An Automatic Verification Framework for Software Configurations

### 2016-05-08 OSDI/abs.tex
better

\app is capable of detecting various tricky errors that cannot
be detected by previous efforts,
including ordering errors, fine-grained value correlation errors, 
entry missing errors, and environment related errors. 
%Our tool, named \app, relies on an abstract representation of language 
%rules to allow for this modularity. 
\ennan{One or two sentences here describe the most important
experimental results. For example, we verify real-world misconfiguration 
files and find 95\% errors are detected.}

>>>>

\app is capable of detecting various tricky errors that cannot
be detected by previous efforts,
including ordering errors, fine-grained value correlation errors, 
entry missing errors, and environment-related errors. 
%Our tool, named \app, relies on an abstract representation of language 
%rules to allow for this modularity. 
\ennan{One or two sentences here describe the most important
experimental results. For example, we verify real-world misconfiguration 
files and find 95\% errors are detected.}

### 2016-05-08 OSDI/intro.tex
some comments
better

In order to truly achieve automatic configuration verification,
we argue that we need to leverage a collection of more powerful learning 
algorithms (not necessarily depending on templates) to derive 
a more sophisticated language model (with abundant rules covering
tricky configuration errors), and then check the configuration files
of interest through the learned language model. \jon{Too many parentheses in setence. Cut down}

@@

Building such an automatic verification framework for
configuration files, nevertheless, requires addressing several challenges. 
Firstly, in order to formulate a correct language model, 
we need to infer each entry's type in a given configuration file, but 
the type of a variable cannot always be fully determined 
from a single value. 
For example, an entry {\tt foo = MAX\_SIZE} is most likely
an integer rather than string; however, existing type inference 
work would report this is an error, because {\tt foo} should be assigned
an integer~\cite{zhang14encore}. \jon{Unclear what the error is. Be more precise} We address this problem by introducing 
so called {\emph{probabilistic types}}.
Rather than assigning only one variable to a single type, 
we assign several types with their probability distributions. 
The entry in the above example might be assigned 
a probabilistic type like 
{\tt \{foo, MAX\_SIZE, [(Int, 60\%), (String, 40\%)]\}}.
With such probabilistic types in hand,
we can generate a more accurate language model,
thus significantly improving our checking capability.

Second, without template, how to learn rules and constraints present
a difficult. \ennan{Here, we need to add one-paragraph description 
to illustrate how we learn rules without templates, 
or why we say our learning results are better than existing
learning approach, \eg, EnCore.}

@@

From a practical perspective, 
\app introduces no additional burden 
to the users: they can simply use \app to check for errors in their
configuration files. However, they can also easily extend the framework
themselves. The system is designed to be highly modular. If there is a
class of rules that \app is not currently learning, the user can develop
their own templates and learners for that class. The new learner can be
added to \app and this way it can check additionally a new set of
errors.

Our \app prototype still has a few limitations:
for example, we cannot handle configuration errors that can be only
triggered in system execution time.
Nevertheless, we believe \app may suggest a practical path
toward automatic and modular language-based configuration verification.
To summarize, this tool paper makes the following contributions:

@@

\item \app employs a collection of machine learning algorithms to 
enable powerful rule and constraint inference without the assistance 
from any pre-defined templates.

\item \app is capable of detecting various tricky errors that cannot
be detected by previous efforts,
including ordering errors, fine-grained value correlation errors, 
entry missing errors, and environment related errors.

>>>>

In order to truly achieve automatic configuration verification,
we argue that we need to leverage a collection of more powerful learning 
algorithms (not necessarily depending on templates) to derive 
a more sophisticated language model (with abundant rules covering
tricky configuration errors), and then check the configuration files
of interest through the learned language model. \jon{Too many parentheses in sentence. Cut down}

@@

Building such an automatic verification framework for
configuration files, nevertheless, requires addressing several challenges. 
Firstly, in order to formulate a correct language model, 
we need to infer each entry's type in a given configuration file, but 
the type of a variable cannot always be fully determined 
from a single value. 
For example, an entry {\tt foo = MAX\_SIZE} is most likely
an integer rather than string; however, existing type inference 
work would report this is an error, because {\tt foo} should be assigned
an integer~\cite{zhang14encore}. \jon{Unclear what the error is. Be more precise} We address this problem by introducing 
{\emph{probabilistic types}}.
Rather than assigning only one variable to a single type, 
we assign several types with their probability distributions. 
The entry in the above example might be assigned 
a probabilistic type like 
{\tt \{foo, MAX\_SIZE, [(Int, 60\%), (String, 40\%)]\}}.
With such probabilistic types in hand,
we can generate a more accurate language model,
thus significantly improving our checking capability.

Secondly, without templates, learning rules and constraints is a challenge. 
\ennan{Here, we need to add one-paragraph description 
to illustrate how we learn rules without templates, 
or why we say our learning results are better than existing
learning approach, \eg, EnCore.}

@@

From a practical perspective, 
\app introduces no additional burden 
to the users: they can simply use \app to check for errors in their
configuration files. However, they can also easily extend the framework
themselves. The system is designed to be highly modular. If there is a
class of rules that \app is not currently learning, the user can develop
her own templates and learners for that class. The new learner can be
added to \app and this way it can check an additional new set of
errors.

Our \app prototype still has a few limitations:
for example, we cannot handle configuration errors that can be 
triggered during system execution time.
Nevertheless, we believe \app may suggest a practical path
toward automatic and modular language-based configuration verification.
To summarize, this tool paper makes the following contributions:

@@

\item \app employs a collection of machine learning algorithms to 
enable powerful rule and constraint inference without assistance 
from any pre-defined templates.

\item \app is capable of detecting various tricky errors that cannot
be detected by previous efforts,
including ordering errors, fine-grained value correlation errors, 
entry missing errors, and environment-related errors.
